Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-09 docs/google-research-awards-latam/main.tex
another pass proposal

JavaScript is one of the most popular programming languages of
today~\cite{business-insider,stackify}. Although the languagre is used
in several application domains, its niche is front-end and back-end
web development\Comment{, supported several frameworks and runtimes
  (\eg{}, Express.js and Node.js)}.

Demands for new features occur in JavaScript as in other popular
programming languages. Recently, the JavaScript specification went
through a more severe change, called by the name ECMAScript6
(ES6)~\cite{es6-features}. Compliance with the new standard is
important for every engine implementation (\eg{}, Google's
V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
Chakra\Fix{cite}) because of
portability~\cite{kangax}.

%\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{11.75cm}
    \centering \textit{The goal of this project is to find bugs in
      implementations of JavaScript engines by leveraging the diversity
      across implementations.}
  \end{minipage}
}
\end{center}
%\vspace{-1ex}

Changes in the language specification often demand sensible changes in
implementations that can result in regressions. Several of these
regression have been reported, some of which were reported by our team
(confirmed by engine developers) using a prototype of our solution
(see Section~\ref{sec:results}).

\section{Design Space}

Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation\Fix{cite}, grammar\Fix{cite}, and random\Fix{cite}) and
whether or not coverage information is taken into account in the
fuzzing process.\Fix{elaborate...}

>>>>

JavaScript is one of the most popular programming languages of
today~\cite{business-insider,stackify}. Its niche is front-end and
back-end web development\Comment{, supported several frameworks and
  runtimes (\eg{}, Express.js and Node.js)}, although the languagre
has been used in other contexts.

Recently, the JavaScript specification went through a bigger change
compared to prior releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. This is natural as requests for new
features are common in popular programming languages. Because of
portability~\cite{kangax}, compliance with the new standard is
important for every engine implementation (\eg{}, Google's
V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
Chakra\Fix{cite}).

%\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{11.75cm}
    \centering \textit{The goal of this project is to find bugs in
      implementations of JavaScript engines by leveraging diversity
      across implementations.}
  \end{minipage}
}
\end{center}
%\vspace{-1ex}

As in any piece of software, changes in the specification often demand
sensible changes in implementations that could lead to regressions. In
fact, several of these regressions have been reported, some of which
were reported by our team (confirmed by engine developers; see
Section~\ref{sec:results}) using a prototype of our solution (see
Section~\ref{sec:design}).

\section{Design Space}
\label{sec:design}

Fuzzing is a popular technique to generate new test inputs from
existing inputs\Fix{cite} with the typical goal of finding
crashes. Several fuzzing methods have been proposed in the past,
varying with respect to how new inputs are generated (\eg{},
mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
random-based\Fix{cite}) and whether or not coverage information is
taken into account in the fuzzing process.\Fix{elaborate...}

\begin{figure}[htbp]
  \centering
  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Workflow of Infrastructure.}
\end{figure}
